Safe Memory Regions for Big Data Processing

### 2016-10-20 paper/introduction.tex
expanded type inference discussion in intro

\paragraph{Type Inference.}
One of the novel contributions of this paper is a sound type inference algorithm
that eliminates the need for users to write region type annotations.
This, we believe, significantly reduces the impediment to adopt our
approach in practical setting.
Our inference algorithm proceeds in two stages: in the first stage,
we introduce region parameters (for classes and methods), and in
the second stage we infer the outlives constraints between these
parameters (using an interprocedural fixed point computation).
% While the first

>>>>

\paragraph{Type Inference.}
One of the key contributions of this paper is a sound type inference algorithm
that eliminates the need for users to write region type annotations.
The users write programs in the underlying language that provides
primitives for the users to manipulate regions (create, open, free,
transfer) and to allocate objects in regions, but has no region type
annotations.
% This, we believe, significantly reduces the impediment to adopt our
% approach in practical setting.

Our inference algorithm proceeds in three stages: in the first stage,
we elaborate the program by introducing region parameters (for classes and methods);
in the second stage we generate a set of constraints that must be satisfied for
the program to type check; in the third stage, we solve the set of constraints,
inferring the preconditions of all classes and methods (in terms of the
expected outlives-constraints between the region parameters).
We show that the second and third stages are sound as well as
complete (while the first stage is sound).
% (using an interprocedural fixed point computation).
% While the first
